---
title: "I-literally-can't-take-this-anymore"
author: "Patricia Zito"
date: "2023-05-11"
output: html_document
---

### This is literally at least the 10th time I've done this I'm so done with everything right now I want to ugly cry and punch Hendel Albatorrez I hope you burn in hell 
```{r}
setwd("/Users/pzito/Desktop/botany563-final/data/orthologs/CURATION5-no-mito-no-chimeric-add-C.elegans")
data <- read.csv("orthologs_filtered_CONSERVED+outgroups-mito.csv")

library(dplyr)
library(stringr)
```

## write new fasta names 
```{r}
fasta.names <- c()
for(i in 1:nrow(data)){
  species <- str_replace(data[i, "species"], " ", "-")
  fasta.name <- paste(paste(">", species, sep = ""), data[i, "protein.accession"], sep = "-")
  fasta.names <- append(fasta.names, fasta.name)
}
data <- cbind(data, fasta.names)

head(data[,c("fasta.names", "species", "protein.accession", "comments")])
dim(data)
```

## remove c.elegans 
```{r}
colnames(data)
as_tibble(data)
data2 <- data %>% filter(species!="Caenorhabditis elegans")
dim(data2)
```

## function
```{r}
write_fasta <- function(df, type, out_name){
  sink(out_name)
  if(type == "protein"){
    for (i in 1:nrow(df)){
      cat(df$fasta.names[i])
      cat("\n")
      cat(df$protein.sequence[i])
      cat("\n")
    }} else if(type == "cds"){
      for (i in 1:nrow(df)){
        cat(df$fasta.names[i])
        cat("\n")
        cat(df$cds.seq[i])
        cat("\n")
      }} else {
      print("type must be either protein or cds")
    }
  sink()
  }
```


## write new fasta and csv files
need a new csv file because new fasta names 
```{r, eval = FALSE}
write.csv(data2, file = "orthologs_filtered_CONSERVED+tardigradesONLY-mito.csv")
write_fasta(data2, type="protein", "orthologs_filtered_CONSERVED+tardigradesONLY-mito-PROTEIN.fasta")
write_fasta(data2, type="cds", "orthologs_filtered_CONSERVED+tardigradesONLY-mito-CDS.fasta")
```


## side project: where is the extra insertion in NHA3 coming from? 
```{r}
# ranges 
nha1 <- seq(49671173, 49673572)
nha2 <- seq(49693946, 49697365)
nha3 <- seq(49719723, 49724026)
nha4 <- seq(49754150, 49757575)
nha5 <- seq(49764468, 49768153)
nha6 <- seq(49775192, 49777995)
nha7 <- seq(49811569, 49809476)
nha8 <- seq(66735544, 66744226)

# now check the results
res_starts <- c(49719729, 49755188, 49810002, 49766737, 49776157, 49723838, 49720746, 49720874, 49719414, 49723297)

for(i in 1:length(res_starts)){
  print(res_starts[i])
  if(res_starts[i] %in% nha1){
    print("contained within nha1")
  } else if(res_starts[i] %in% nha2){
    print("contained within nha2")
  } else if(res_starts[i] %in% nha3){
    print("contained within nha3")
  } else if(res_starts[i] %in% nha4){
    print("contained within nha4")
  } else if(res_starts[i] %in% nha5){
    print("contained within nha5")
  } else if(res_starts[i] %in% nha6){
    print("contained within nha6")
  } else if(res_starts[i] %in% nha7){
    print("contained within nha7")
  } else if(res_starts[i] %in% nha8){
    print("contained within nha8")
  } else {
    print("not contained in any of the nhas")
  }
}